---
title: "Introducing Rfiglet"
author: "Drew Schmidt"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: true
    toc: false
    number_sections: false
    css: include/custom.css
    highlight: kate
vignette: >
  %\VignetteIndexEntry{Introducing Rfiglet}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, echo = FALSE, message = FALSE}
library(Rfiglet)
options(scipen = 3)
knitr::opts_chunk$set(
  comment = NA,
  error   = FALSE,
  tidy    = FALSE)
```

```{r, echo=FALSE}
library(Rfiglet)

font <- "standard"
header <- c(figlet("Introducing", font=font), figlet("Rfiglet", font=font))
class(header) <- "figlet"

header
```


This work is licensed under a [Creative Commons Attribution 4.0 International License](http://creativecommons.org/licenses/by/4.0/)



# Introduction

[figlet](http://www.figlet.org/), which stands for "Frank, Ian, and Glenn's LETters", is a well-known terminal utility for generating ascii banners.  For example, in the terminal, you might do something like:

```
$ echo "test" | figlet
 _            _   
| |_ ___  ___| |_ 
| __/ _ \/ __| __|
| ||  __/\__ \ |_ 
 \__\___||___/\__|
                  
```

The **Rfiglet** package is a set of bindings for using figlet from R.

```{r}
library(Rfiglet)

figlet("test")
```





# Installation

You can install the stable version from CRAN using the usual `install.packages()`:

```r
install.packages("Rfiglet")
```

The development version is maintained on GitHub, and can easily be installed by any of the packages that offer installations from GitHub:

```r
### Pick your preference
devtools::install_github("wrathematics/Rfiglet")
ghit::install_github("wrathematics/Rfiglet")
remotes::install_github("wrathematics/Rfiglet")
```





# Font Selection

There are over 150 fonts available, listed in the package help.
Additionally, you can see exaples from all available fonts in the *Figlet Font Showcase* vignette which also ships with the **Rfiglet** package.

Finally, there is a bundled shiny app "Figlet as a Service" (faas), which allows you to quickly see some text figlet-ized.  You can run it by entering

```r
Rfiglet::faas()
```

Note that this requires you have the shiny package available.





# Details

Printing is handled by a highly modified version of the figlet command line utility.  If you know a thing or two about R calling C functions, have a look at the R source code for the `Rfiglet::figlet()` function for a laugh.

The output is a "line-by-line" vector of strings (like the output of `readLines()`) cast as an S3 class `figlet`, which allows for fancy printing.
